Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-09 paper/paper.tex
minor fix

Other than the the case with real numbers, we have polynomials and truncated polynomials as algebra types. We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
This approach to use generic tensor networks can be easily extended to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}. 
Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
%Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
%We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
By adapting to the style of generic programming, we can implement all the algorithms without much effort.
We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond. This approach of generic tensor networks should also inspire future works on tensor network computations.

>>>>

Other than the the case with real numbers, we have polynomials and truncated polynomials as algebra types.
We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
These algebras are general purposed, they can be used to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}. 
Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
%Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
%We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
By adapting to the style of generic programming, we can implement all the algorithms without much effort.
We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
We expect our tool can be used to understand and study many interesting applications of independent sets and beyond. This approach of generic tensor networks should also inspire future works on tensor network computations.
